\chapter*{Abstract}


This dissertation presents aspects of vision based movement detection, control systems, simulation methodology and test results for a distributed optical position correction scheme for \gls{UAV}. A detailed physical model of a quadrocopter combined with a novel, simple and robust \gls{PID} control approach and a detailed configurable virtual camera environment were realised during this thesis, and provide an innovative method to simulate and test scenarios with different flight trajectories and sensor configurations. The content of this research is the exploratory work for the development of a vision-based stabilisation system for the \gls{HSE} quadrocopter project. 

The first part of this thesis contains the project organisation, the related tools and architectures, and presents the strengths and risks of the used simulation driven methodology. Afterwards, the literature review presents several technical topics of existing \gls{UAV} techniques for vision-based stabilisation, and further methods for mathematical description of a quadrocopter, optical movement detection and suitable control. A detailed analysis of the existing architecture, the corresponding simulation containing the not-purchased vision module and the realisation of control and image processing modules are presented in the design and implementation chapter. Subsequently, test scenarios are derived from a set of vision-based navigation and correction implementations of other projects, and used to analyse the position correction scheme of the \gls{HSE} quadrocopter simulation. The last part of this thesis gives an overview of the results and outcomes, and presents the upcoming projects which will be based on the results of this work. Finally, it gives an overview of the new possibilities to realise high complexity scientific projects using the introduced simulation architecture.