\chapter*{Acknowledgements}

I would like to thank the many people who have supported me and made this Master's Thesis possible. 
My girlfriend Sabine, and my parents Nikolaos and Kiriaki, an endless source of encouragement, support and love.
I am grateful to my supervisor Dr. Marios Hadjinicolaou for his confidence in me and my project, and
the priceless encouragement and support throughout my dissertation. 

Special Thanks to Prof. Dr. Joerg Friedrich for his trust and support, and the chance to be responsible for the quadrocopter project of the Faculty of Information Technology \gls{HSE}. It was an incomparable experience and a great honor. Further, I would like to thank Mr. Wiedenhoefer of the Faculty of Mechatronics, and Prof. Dr. Czarnetzki of the Faculty of Mechanical Engineering, for the great interdisciplinary project collaboration.

A special thanks to my project colleague Peter Beltz for his endless commitment in new quadrocopter developments and his patience to repair the crushed hardware again and again. Also, I am grateful to my project colleague Rafael Trybek for the excellent testing, demonstration flying and his great technical support. 

Thanks to my Master colleagues Daniel Szabo, Florian Theis, Jian Wu and Daniel Tech. It was a great honor to work with you. 

I want to thank Robert Czech for his endless dedication and great support. Finally, a special Thanks to my childhood friend Florian Mueller and to the other persons who have proofread and commented on this document. All remaining mistakes are mine. 